\documentclass[a4paper,10pt]{article}
\usepackage{titlesec}
\usepackage{latexsym,amssymb,amsmath,enumitem}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\geometry{margin=1cm}

% Custom formatting
\titleformat{\section}
  {\large\bfseries\color{black}}{}{0pt}{}[\vspace{-0.1em}]
\titlespacing*{\section}{0pt}{0.6em}{0.2em} % increased before-title space

\newcommand{\sectionline}{\vspace{-0.1em}\noindent\rule{\linewidth}{0.6pt}\vspace{-0.7em}}


\titleformat{\subsection}{\normalsize\bfseries\color{black}}{}{0em}{}
\titleformat{\subsubsection}[runin]{\bfseries}{\thesubsubsection}{1em}{}
\renewcommand{\labelitemi}{--}

\pagestyle{empty}

\begin{document}

%----------------------------------
% Header
%----------------------------------
\begin{center}
  \textbf{\LARGE Devshree Bharatia} \\[3pt]
  City, Country \quad $\vert$ \quad \href{mailto:your.email@domain.com}{your.email@domain.com} \quad $\vert$ \quad Contact No \\[3pt]
  \href{https://github.com}{GitHub Link} \quad $\vert$ \quad \href{https://www.wixsite.com}{Portfolio Link} \quad $\vert$ \quad \href{https://linkedin.com}{LinkedIn Link}
\end{center}

\vspace{-1em}
%----------------------------------
% Education
%----------------------------------
\sectionline
\section*{Education}
\textbf{Georgia Institute of Technology}, Atlanta, GA \hfill \textit{Aug 2021 -- Dec 2022}\\
M.S. in Computer Science (Specialization: Machine Learning) \hfill GPA: 3.9/4 \\
Relevant Coursework: Data Structures, Machine Learning, AI, Computer Vision, Big Data\\
\textbf{University of Pune (SPPU)} \hfill \textit{Jul 2015 -- May 2019}\\
B.E. in Computer Engineering (Gold Medalist) \hfill GPA: 9.48/10
%----------------------------------
% Skills
%----------------------------------
\sectionline
\section*{Skills}
\textbf{Languages \& Frameworks} Python, Java, C/C++, JavaScript, SpringBoot, Node.js, TensorFlow, PyTorch \\
\textbf{Cloud Platforms:} AWS, Microsoft Azure, Google Cloud Platform (GCP), Firebase \\
\textbf{DevOps \& Tools:} Docker, Kubernetes, Jenkins, Git, CI/CD, IntelliJ, VS Code, JIRA, Postman, Grafana \\
\textbf{Databases:} MySQL, Elasticsearch, SQLite \\
%----------------------------------
% Experience
%----------------------------------
\sectionline
\section*{Professional Experience}
\textbf{Walmart}, Software Engineer III \hfill \textit{Feb 2023 -- Present}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item Engineered scalable backend services in Planner, a Java SpringBoot and REST API-based framework, to batch millions of express and scheduled orders into optimized last-mile delivery trips across 500+ locations.
  \item Optimized carrier, van, and driver assignment algorithms, reducing average route time by 18\% and improving delivery success rates in high-volume, time-sensitive environments
\end{itemize}
\textbf{Shoreline IoT}, Software Engineer I \hfill \textit{Jun 2019 -- May 2021}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item Designed Node.js microservices for a smart-gateway IoT device and implemented MQTT-based pub-sub architecture to enable real-time monitoring and scheduling of events via a cloud-based UI.
  \item Awarded “Notable Achievement Award” for leading end-to-end project delivery, resolving critical issues, conducting unit and functional testing and independently managing client communication.
\end{itemize}
\textbf{Schlumberger}, Data Science Intern \hfill \textit{Jun 2018 -- Aug 2018}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item Designed interactive dashboards and reports in Microsoft PowerBI to analyze relational databases at Schlumberger, leveraging advanced features like dynamic query parameters. \item Improved internal data visibility and enabled 25\% faster operational insights for stakeholders
\end{itemize}
%----------------------------------
% Projects
%----------------------------------
\sectionline
\section*{Academic Projects}
\textbf{Visual Reasoning for the Visually Impaired} \hfill \textit{Sep 2021 -- Dec 2021}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item “Developed a deep learning model using PyTorch and TensorFlow to assist blind users in querying their environment via image-based question answering.”
\item Integrated CNNs for object detection and applied BERT for natural language query understanding.
\item Achieved 82\% accuracy on a custom dataset of 1,000 real-world scenarios.
\end{itemize}
\textbf{Smart E-Stick for the Visually Impaired (Best Project Award)} \hfill \textit{Jun 2018 -- May 2019}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item Built an award-winning IoT solution combining a microcontroller-driven e-stick and an Android app to assist visually impaired users with real-time navigation and object detection.
  \item Enabled object detection via CNN and OCR-based text extraction using NLP. The app facilitated live GPS tracking, SOS alerts, and stick location tracking.
\item Recognized as ‘Best Project’ among 70+ teams in the computer science department.
\end{itemize}
%----------------------------------
% Publications
%----------------------------------
\sectionline
\section*{Publications \small\href{https://scholar.google.com/citations?user=MzlxMPMAAAAJ&hl=en}{(Google Scholar)}}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item Bharatia D, \textit{Smart E-Stick for Visually Impaired using Video Intelligence API}, \textbf{IEEE IBSSC 2019}.
  \item Bharatia D,  \textit{Advanced Image Analysis and Its Applications}, \textbf{IEEE GCAT 2019}.
  \item Bharatia D,  \textit{Smart E-Stick using Android App and Cloud Vision}, \textbf{GCAT 2019}.
\end{itemize}
%----------------------------------
% Honors
%----------------------------------
\sectionline
\section*{Honors \& Leadership}
\begin{itemize}[leftmargin=1.5em, itemsep=0.01em]
  \item University Gold Medalist and Overall Topper and all-rounder of the Computer Department for 4 years.
  \item Editorial Head, College Magazine: Led a 10-member team and oversaw ideation, content creation and final publication.
  \item Grad Application Mentor: Helped 1,000+ MS/PhD aspirants refine resumes and SOPs to craft compelling university applications.
  \item Technical Writer, GeeksforGeeks: Authored tech content for India’s leading CS education platform with 5M+ readers.
\end{itemize}
\end{document}
